Modular and Dependent Interpretations for Shallow Embeddings

### 2015-05-03 dAlg/mrm.tex
Improve composition operator for MRM approach

\title{Composable Algebra with Dependencies}
%\subtitle{A List-of-Functors Approach to Two-Level Types}

@@

>>>>

\title{Modular and Dependent Interpretations for Shallow Embeddings}
%\title{Composable Algebra with Dependencies}

@@

\bibitem{oliveira13}
  Oliveira, B.C.d.S., Storm, Tijs van der, Loh, Alex and Cook, William R.
  Feature-Oriented Programming with Object Algebra
  \emph{ECOOP'13 Proceedings of the 27th European conference on Object-Oriented Programming},
  pages 27-51.
  2013
